SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 results.tex
putting it back

% \subsection{Additional Memory Constraints}
% \label{Results-AdditionalMem}

% %Figure~\ref{Fig:AddnConstr}(a) and (b) show the performance of PPF in a
% %followed by the overall performance on the complete benchmark.  
% %For the sake of brevity, we have only shown selected traces

% We also model PPF with reduced LLC and with low bandwidth constraints,
% respectively (not illustrated for space reasons).  % Benchmark {\tt
% % 605.mcf\_s} in low bandwidth conditions is prefetch averse. In
% % general, any prefetcher yields a negative speedup on that trace. On
% % {\tt 654.roms\_s} and {\tt 607.cactuBSSN\_s}, PPF is unable to match
% % the performance achieved by the best prefetcher. On the other hand,
% % PPF outperforms all the other prefetchers on {\tt 623.xalancbmk\_s}
% % and {\tt 638.imagick\_s} benchmarks.
% Overall, PPF provides a greater improvement under small LLC condition
% and matches the best prefetcher, BOP, under low DRAM bandwidth
% conditions.

>>>>

\subsection{Additional Memory Constraints}
\label{Results-AdditionalMem}

%Figure~\ref{Fig:AddnConstr}(a) and (b) show the performance of PPF in a
%followed by the overall performance on the complete benchmark.  
%For the sake of brevity, we have only shown selected traces

We also model PPF with reduced LLC and with low bandwidth constraints,
respectively (not illustrated for space reasons).  Benchmark {\tt
  605.mcf\_s} in low bandwidth conditions is prefetch averse. In
general, any prefetcher yields a negative speedup on that trace. On
{\tt 654.roms\_s} and {\tt 607.cactuBSSN\_s}, PPF is unable to match
the performance achieved by the best prefetcher. On the other hand,
PPF outperforms all the other prefetchers on {\tt 623.xalancbmk\_s}
and {\tt 638.imagick\_s} benchmarks.  Overall, PPF provides a greater
improvement under small LLC condition and matches the best prefetcher,
BOP, under low DRAM bandwidth conditions.
